\texttt{DreamCoder}: Growing libraries of concepts with wake-sleep program induction

### 2018-10-04 pp.tex
possibly final talk slides

\documentclass{beamer} 
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\begin{frame}{Growing a domain-specific language of thought}

@@

  \pause
  \vspace{1cm}

  \begin{itemize}
  \item Library of concepts (declarative knowledge)
    \item Inference strategy (procedural knowledge)
    \end{itemize}
\end{frame}

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Combines ideas from Wake-Sleep \& Exploration-Compression algorithm by Eyal Dechter
\Wider[5.4em]{
  \begin{tikzpicture}
    \node at (6,0) {  \includegraphics[width = 4cm]{figures/sleepingChild.jpg}};
    \visible<2->{
      \node(Lisp) at (-3,0) {\includegraphics[width = 3cm]{figures/Lisp.png}};
      \node(tower) at ([xshift=1.5cm]Lisp.east) {\includegraphics[width = 3cm]{figures/pyramid1.png}};
      \node(logo) at ([xshift=1.5cm]tower.east) {\includegraphics[width =3cm]{figures/9logo.png}}; 
    }
    \end{tikzpicture}}

@@

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}

  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 4 6)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 18 4)}\\
    \end{tabular}&

@@

    \\\bottomrule
  \end{tabular}

@@

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}

  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2)}$\to$\texttt{(2 4)}\\
      \texttt{(1 9)}$\to$\texttt{(2 18)}\\
    \end{tabular}&
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z z)))}
      \end{tabular}

    \begin{tabular}{l}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2)}$\to$\texttt{(2 3)}\\
      \texttt{(1 9)}$\to$\texttt{(2 10)}\\
    \end{tabular}&
    \begin{tabular}{l}
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z 1)))}
      \end{tabular}
    \end{tabular}

    \\\bottomrule
  \end{tabular}

@@

    \node[draw](m) at (2,-7) {
\begin{tabular}{l}
          \texttt{\emph{map}} = \orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(cons (f (car l))}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(r (cdr l))))))}}
      \end{tabular}      
    };
    \draw [->](r1.south)--(m.north);
    \draw [->](r2.south)--(m.north);
    \node[fill=white] at ([yshift=0.5cm]m.north) {\textbf{Compress (MDL/Bayes objective)}};
    \visible<2-3>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $10^{14}$\\\Huge  refactorings };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $10^{13}$\\\Huge  refactorings };
    }
    \visible<3>{
      \node[fill=orange!50!white,align=center] at ([yshift=7cm]m.north) {\Huge version space: set of programs\\
      \huge Lau 2003; Gulwani 2012};
      }
    \visible<4>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $\leq 10^6$\\\Huge version spaces };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $\leq 10^6$\\\Huge version spaces };
    }
    \end{tikzpicture}
    }
  \end{frame}

@@

  Discovers 38 concepts, including `filter'. With different tasks will also learn `map', `fold', `unfold', etc. starting with 1950's Lisp
\end{frame}

@@

@@

\begin{frame}{Turtle graphics --- \small{Created \& investigated by Mathias
  Sablé--Meyer}}

@@

  \only<1>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \vspace*{5\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/line.eps}
    \end{columns}
  }
  \only<2>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle.eps}
    \end{columns}
  }
  \only<3>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{1\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle2.eps}
    \end{columns}
  }
  \only<4>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(4)}\\
          \texttt{> FW 1}\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/square.eps}
    \end{columns}
  }
  \only<5>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> FW 1} \\
          \texttt{> SET origin} \\
          \texttt{> RT} $\frac{2\pi}{8}$\\
          \vspace*{2\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/star.eps}
    \end{columns}
  }
  \only<6>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> PU} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> PD} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{0\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/spiral.eps}
    \end{columns}
  }
  \only<7>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range($\infty$)}\\
          \texttt{> FW $\varepsilon$}\\
          \texttt{> RT} $\varepsilon$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/circle.eps}
    \end{columns}
  }
  \visible<7>{
    \vspace{0.2cm}
    \texttt{\alert{NUM} ::= 1 | $\pi$ | $\infty$ | $\varepsilon$ | + | - | * | / }
  }
\end{frame}

@@

\begin{frame}{Turtle graphics --- Learning curves}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalkLC.eps}
  \begin{itemize}
    \item $\frac\pi2$ and $\frac\pi4$ from $\pi$, $2$, $+$ and $/$
    \item A line of length \texttt{n} followed with a right angle
    \item Loops of length \texttt{n} that uses the number \texttt{n} inside.
    \item Unit line then teleport back to origin
    \item ...
  \end{itemize}
\end{frame}

@@

\begin{frame}{Turtle graphics --- More dreams, 5 minutes, 1st iteration}
  \centering
  \includegraphics[width=8cm]{figures/dreams/5m_firstIteration.eps}
\end{frame}

\begin{frame}{Turtle graphics --- More dreams, 5 minutes, last iteration}
  \centering
  \includegraphics[width=8cm]{figures/dreams/5m_final.eps}
\end{frame}

\begin{frame}{Turtle graphics --- Dreaming from learned generative model}
  \centering
  \only<1>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/1.png}
    \end{figure}
  }
  \only<2>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/2.png}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/3.png}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/4.png}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/6.png}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/7.png}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/8.png}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/9.png}
    \end{figure}
  }
\end{frame}
\begin{frame}{Tower building in blocks world}
  \large
\centering  
  Control a hand that puts down blocks \\
  \hspace{1cm}(turtle: control a pen that puts down ink)
\only<1>{\includegraphics[width = \textwidth]{figures/3t.png}}
\only<2>{\includegraphics[width = 0.6\textwidth]{figures/every_tower.png}}

@@

>>>>

\documentclass{beamer} 
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\greenCode}[1]{{\footnotesize\popp{\code{#1}}}}
\newcommand{\blueCode}[1]{{\footnotesize\pop{\code{#1}}}}

\usepackage{pgf}

@@

\begin{frame}{Growing domain-specific knowledge}

@@

  \begin{itemize}
  \item Library of concepts (declarative knowledge; generative model over programs)
    \item Inference strategy (procedural knowledge)
  \end{itemize}
  \only<2>{
  \begin{tikzpicture}
    \node(problem) at (0,0) {\includegraphics[width = 2cm]{figures/functions/48.png}};
    \node(synthesizer)[draw,align=center] at ([xshift=3cm]problem.east) {Learned \\program inducer};
    \draw[->] (problem.east) -- (synthesizer.west);
    \node(program)[draw, align=center] at ([xshift=3cm]synthesizer.east) {program:\\$f(x) = 0.7x^2+1.2$};
    \draw[->] (synthesizer.east) -- (program.west);
  \end{tikzpicture}}
    \renewcommand\code\texttt
    \only<3>{
\Wider[4em]{  \begin{tikzpicture}
    \node[draw,align=center](problem) at (0,0) {
            \begin{tabular}{l}
          \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} \\
          \end{tabular}
};
    \node(synthesizer)[draw,align=center] at ([xshift=2.5cm]problem.east) {Learned \\program inducer};
    \draw[->] (problem.east) -- (synthesizer.west);
    \node(program)[draw, align=center] at ([xshift=2.5cm]synthesizer.east) {program:\\\code{(filter ($\lambda$ (x)}\\\code{ (> x 2)))}};
    \draw[->] (synthesizer.east) -- (program.west);
  \end{tikzpicture}

  \vspace{0.5cm}Concepts: \code{filter}, etc\\Inference strategy: neurosymbolic search for programs
    }}

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Combines ideas from Wake-Sleep \& Exploration-Compression algorithm by Eyal Dechter
\Wider[5.4em]{
  \begin{tikzpicture}
    \node at (6,0) {  \includegraphics[width = 4cm]{figures/sleepingChild.jpg}};
    \visible<2->{
      \node(Lisp) at (-3,0) {\includegraphics[width = 3cm]{figures/Lisp.png}};
      \node[align=center](tower) at ([xshift=1cm]Lisp.east) {\includegraphics[width = 1cm]{figures/functions/627.png}\hspace{0.05cm}\includegraphics[width = 1cm]{figures/functions/615.png}\\
        \includegraphics[width = 1cm]{figures/functions/382.png}\hspace{0.05cm}\includegraphics[width = 1cm]{figures/functions/0.png}%
      };
      \node(logo) at ([xshift=1.5cm]tower.east) {\includegraphics[width =3cm]{figures/9logo.png}}; 
    }
    \end{tikzpicture}}

@@

\begin{comment}

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}
  \Wider[5.4em]{
  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 4 6)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 18 4)}\\
    \end{tabular}&

@@

    \\\bottomrule
  \end{tabular}}

@@

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}
    \Wider[5.4em]{
  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 4 6)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 18 4)}\\
    \end{tabular}&
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z z)))}
      \end{tabular}

    \begin{tabular}{l}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 3 4)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 10 3)}\\
    \end{tabular}
    &
    \begin{tabular}{l}
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z 1)))}
      \end{tabular}
    \end{tabular}

    \\\bottomrule
  \end{tabular}}

@@

    \node[draw](m) at (2,-7) {
\begin{tabular}{l}
          \texttt{\emph{map}} = \orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(cons (f (car l))}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(r (cdr l))))))}}
      \end{tabular}      
    };
    \draw [->](r1.south)--(m.north);
    \draw [->](r2.south)--(m.north);
    \node[fill=white] at ([yshift=0.5cm]m.north) {\textbf{Compress (MDL/Bayes objective)}};
    \visible<2-3>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $10^{14}$\\\Huge  refactorings };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $10^{13}$\\\Huge  refactorings };
    }
    \visible<3>{
      \node[fill=orange!50!white,align=center] at ([yshift=7cm]m.north) {\Huge version space: set of programs\\
      \huge Lau 2003; Gulwani 2012};
      }
    \visible<4>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $\leq 10^6$\\\Huge version spaces };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $\leq 10^6$\\\Huge version spaces };
    }
    \end{tikzpicture}
    }
\end{frame}
 \end{comment}

@@

  Discovers 38 concepts, including `filter'. %With different tasks will also learn `map', `fold', `unfold', etc. starting with 1950's Lispthe

\begin{picture}(50,70) \put(250,0){\hbox{\includegraphics[width = 3cm]{figures/Lucas}}} \end{picture} 
\end{frame}
\begin{frame}{Learning the basics of programming}
  \includegraphics[width = \textwidth]{figures/McCarthy.png}

\centering  McCarthy 1959 Lisp  $\longrightarrow$ Modern functional programming

  22 tasks. 64 CPUs. 93 hours.

@@

\begin{frame}{Learned text processing DSL}
  \only<1>{  \includegraphics[width = \textwidth]{figures/textPrimitives.pdf}}
  \only<2>{  \includegraphics[width = \textwidth]{figures/textPrimitives.png}}

@@

\begin{frame}{Turtle graphics --- \small{Created \& investigated by Mathias
      Sablé--Meyer}}
    \begin{picture}(50,50) \put(280,-20){\hbox{\includegraphics[width = 2cm]{figures/French}}} \end{picture} \vspace{-2cm}

@@

  \only<1>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \vspace*{5\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/line.eps}
    \end{columns}
  }
  \only<2>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle.eps}
    \end{columns}
  }
  \only<3>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{1\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle2.eps}
    \end{columns}
  }
  \only<4>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(4)}\\
          \texttt{> FW 1}\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/square.eps}
    \end{columns}
  }
  \only<5>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> FW 1} \\
          \texttt{> SET origin} \\
          \texttt{> RT} $\frac{2\pi}{8}$\\
          \vspace*{2\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/star.eps}
    \end{columns}
  }
  \only<6>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> PU} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> PD} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{0\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/spiral.eps}
    \end{columns}
  }
  \only<7>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range($\infty$)}\\
          \texttt{> FW $\varepsilon$}\\
          \texttt{> RT} $\varepsilon$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/circle.eps}
    \end{columns}
  }
  \visible<7>{
    \vspace{0.2cm}
    \texttt{\alert{NUM} ::= 1 | $\pi$ | $\infty$ | $\varepsilon$ | + | - | * | / }
  }

@@

\begin{frame}{Turtle graphics --- Learning curves}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalkLC.eps}
  %% \begin{itemize}
  %%   \item $\frac\pi2$ and $\frac\pi4$ from $\pi$, $2$, $+$ and $/$
  %%   \item A line of length \texttt{n} followed with a right angle
  %%   \item Loops of length \texttt{n} that uses the number \texttt{n} inside.
  %%   \item Unit line then teleport back to origin
  %%   \item ...
  %% \end{itemize}
\end{frame}

\begin{frame}{Turtle graphics --- Illustration of learned DSL}

  \only<1>{\centering\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_4.png}}
  \only<2>{\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_1.png}}
  \only<3>{\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_7.png}}
  \only<4>{\centering\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_12.png}}
  \only<5>{\centering\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_14.png}}
  \only<6>{\centering\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_5.png}}
  \only<7>{\centering\includegraphics[width = \textwidth]{figures/logo_primitives/logo_primitive_13.png}}

@@

%% \begin{frame}{Turtle graphics --- More dreams, 5 minutes, 1st iteration}
%%   \centering
%%   \includegraphics[width=8cm]{figures/dreams/5m_firstIteration.eps}
%% \end{frame}

%% \begin{frame}{Turtle graphics --- More dreams, 5 minutes, last iteration}
%%   \centering
%%   \includegraphics[width=8cm]{figures/dreams/5m_final.eps}
%% \end{frame}

\begin{frame}{Turtle graphics --- Dreaming from learned generative model}
  \centering
  \only<1>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/1.png}
    \end{figure}
  }
  \only<2>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/2.png}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/3.png}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/4.png}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/6.png}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/7.png}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/8.png}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/9.png}
    \end{figure}
  }
\end{frame}

\begin{comment}
\begin{frame}{Tower building in blocks world}
  \large
\centering  
  Control a hand that puts down blocks \\
  \hspace{1cm}(turtle: control a pen that puts down ink)
\only<1>{\includegraphics[width = \textwidth]{figures/3t.png}}
\only<2>{\includegraphics[width = 0.6\textwidth]{figures/every_tower.png}}

@@

\end{frame}
  \end{comment}
